Reproducible Results in Parsing-Based Machine Translation:\\ The JHU Shared Task Submission

### 2010-04-22 papers/wmt10.pipeline/paper.tex
More work
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1598 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\documentclass[11pt]{article}
%\usepackage[%
%  colorlinks,%
%  linkcolor=black,%
%  anchorcolor=black,%
%  citecolor=black,%
%  filecolor=black,%
%  menucolor=black,%
%  pagecolor=black,%
%  urlcolor=black,%
%  %hyperindex=false,%
%  bookmarksopen=true,%
%  pdfusetitle,%
%  pdfpagelabels,
%  naturalnames
%]{hyperref}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

%\usepackage[colorlinks]{hyperref}

\usepackage{tikz}
\usetikzlibrary{fit,shapes.misc,shapes}

\usepackage{acl2010}
\usepackage[colorinlistoftodos]{todonotes}

%\title{Empirical Questions in Machine Translation\
 %--- Reproducible Results for the JHU WMT10 System}
\title{Reproducible Results in Parsing-Based Machine Translation:\\
The JHU Shared Task Submission}

@@

%\listoftodos

@@

%\todo[inline,color=yellow,caption={Call to action}]{

@@

The last four years have witnessed the implementation and release of numerous open source machine translation systems. The widely used Moses system implements the standard phrase-based translation model. Parsing-based translation models are implemented by SAMT \cite{samt2006} and Joshua \cite{Joshua-WMT}. Cunei \cite{Phillips2009} implements statistical example-based translation. The SRILM \cite{Stolcke2002} and IRSTLM \cite{IRSTLM} toolkits enable efficient training and querying of n-gram language models. \newcite{Phramer} and \newcite{schwartz08mclc} provide other open-source implementations of phrase-based and hierarchical decoders, respectively.

@@

Systems to address the complex workflows required to run non-trivial machine translation experiments have also been developed. These include {\tt experiment.perl} \cite{experiment.perl}, developed as a workflow management system at the University of Edinburgh, and LoonyBin \cite{LoonyBin}, a general hyperworkflow management utility from Carnegie Melon University.

\todo[inline,caption={Parsing-based SMT}] {
Hiero grammar extraction \cite{Lopez2008}
}

@@

%\missingfigure{Graph of dependencies and steps}
\begin{figure*}
%\include{mt-workflow-preprocess}
\include{figure.pgf}
%\begin{tikzpicture}[shape=rounded rectangle]
%\node (PreprocessLabel) {\underline{\bf Preprocess Data}};
%\node (CompressedData) [style=draw,below of= PreprocessLabel]  {Compressed Data};
%\node (DecompressedData) [style=draw,below of=CompressedData] {Decompressed Data};a
%\node (RemoveXML) [style=draw,below of=DecompressedData,text width=28mm]  {Test Set Data Stripped of XML};
%\node (Tokenize) [style=draw,below of= RemoveXML]  {Tokenized Data};
%\node (Normalize) [style=draw,below of=Tokenize] {Normalized Data};
%\node [style=draw,shape=rectangle,fit=(PreprocessLabel) (CompressedData) (DecompressedData) (RemoveXML) (Tokenize) (Normalize)] {};
%
%\draw [->] (CompressedData) -- (DecompressedData);
%\draw [->] (DecompressedData) -- (RemoveXML);
%\draw [->] (RemoveXML) -- (Tokenize);
%\draw [->] (Tokenize) -- (Normalize);
%\draw [->] (DecompressedData) -- (Tokenize);
%\end{tikzpicture}

\caption{Machine translation workflow. The scripts and configuration files used to implement and run this workflow are available for download at \url{http://sourceforge.net/projects/joshua/files/joshua/1.3/wmt2010-experiment.tgz}}
\end{figure*}

>>>>

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{tikz}
\usetikzlibrary{fit,shapes.misc,shapes}
\usepackage{acl2010}
\usepackage[colorinlistoftodos]{todonotes}

\title{Reproducible Results in Parsing-Based Machine Translation:\\
The JHU Shared Task Submission}

@@

@@

@@

The last four years have witnessed the implementation and release of numerous open source machine translation systems. The widely used Moses system implements the standard phrase-based translation model. Parsing-based translation models are implemented by Joshua \cite{Joshua-WMT} and SAMT \cite{samt2006}. Cunei \cite{Phillips2009} implements statistical example-based translation. \newcite{Phramer} and \newcite{schwartz08mclc} respectively provide additional open-source implementations of phrase-based and hierarchical decoders.

The SRILM \cite{Stolcke2002}, IRSTLM \cite{IRSTLM}, and RandLM \cite{Talbot2007a} toolkits enable efficient training and querying of n-gram language models.

@@

Open source systems to address the complex workflows required to run non-trivial machine translation experiments have also been developed. These include {\tt experiment.perl} \cite{experiment.perl}, developed as a workflow management system at the University of Edinburgh, and LoonyBin \cite{LoonyBin}, a general hyperworkflow management utility from Carnegie Melon University.

@@

\begin{figure*}
\include{figure.pgf}

\caption{Machine translation workflow. Nodes in grey indicate software and scripts. The scripts and configuration files used to implement and run this workflow are available for download at \url{http://sourceforge.net/projects/joshua/files/joshua/1.3/wmt2010-experiment.tgz}}
\end{figure*}
